Parsing Tweets into Universal Dependencies

### 2018-04-16 paper.tex
revise the citation in our baseline.

Social media applications typically require processing large volumes
of data, making speed an important consideration. We therefore 
begin with the neural greedy stack LSTM parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
which can parse a sentence in linear time and harnesses 
character representations to construct word vectors, which should help mitigate the challenge of
spelling variation. We encourage the reader to refer their paper for
more details about the model.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rccc}
%		\hline
		\it System & UAS & LAS & Kt/s \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} & 81.4 & 76.9 & 0.3 \\
		\citet{dozat-qi-manning:2017:K17-3} & 81.8 & 77.7 & 1.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.7 & 2.3 \\
		\hdashline
		Ensemble (20) & 83.4 & 79.4 & 0.2 \\
		Distillation ($\alpha =1.0$) & 81.8 & 77.6 & 2.3 \\
		Distillation ($\alpha =0.9$) & 82.0 & 77.8 & 2.3 \\		
		Distillation w/ exploration & 82.1 & 77.9 & 2.3 \\
%		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2} test set,
           with automatic POS tags. The ``Kt/s'' column shows
           the parsing speed evaluated by thousands of tokens
           the model processed per second.
            \label{tbl:parse-result}}
\end{table}

>>>>

Social media applications typically require processing large volumes
of data, making speed an important consideration. We therefore 
begin with the neural greedy stack LSTM parser introduced by \cite{ballesteros-dyer-smith:2015:EMNLP},
which can parse a sentence in linear time and harnesses 
character representations to construct word vectors, which should help mitigate the challenge of
spelling variation. We encourage the reader to refer their paper for
more details about the model.

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rccc}
%		\hline
		\it System & UAS & LAS & Kt/s \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} & 81.4 & 76.9 & 0.3 \\
		\citet{dozat-qi-manning:2017:K17-3} & 81.8 & 77.7 & 1.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\hdashline
		%\citet{ballesteros-EtAl:2016:EMNLP2016} & & & \\
		\citet{ballesteros-dyer-smith:2015:EMNLP} & 80.2 & 75.7 & 2.3 \\
		Ensemble (20) & 83.4 & 79.4 & 0.2 \\
		Distillation ($\alpha =1.0$) & 81.8 & 77.6 & 2.3 \\
		Distillation ($\alpha =0.9$) & 82.0 & 77.8 & 2.3 \\		
		Distillation w/ exploration & 82.1 & 77.9 & 2.3 \\
%		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2} test set,
           with automatic POS tags. We use \citet{ballesteros-dyer-smith:2015:EMNLP}
           as our baseline and build the ensemble and distilling model over it.
           The ``Kt/s'' column shows
           the parsing speed evaluated by thousands of tokens
           the model processed per second.
            \label{tbl:parse-result}}
\end{table}
